---
title: "New York Air Quality Measurements"
author: "Nishant Sisingi"
date: "October 15, 2016"
output: 
  ioslides_presentation: 
    smaller: yes
    widescreen: true
    incremental: true
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



## Data Description
<div class="green">
>- Daily air quality measurements in New York, May to September 1973.  

>- The data were obtained from the New York State Department of Conservation (ozone data) and the National Weather Service (meteorological data)

```{r}
library(tibble)
data("airquality")
attach(airquality)
airquality <- as_tibble(airquality)
airquality

```
</div>

## App Objectives 
<div class="green">
>- Observe the effects of various variables, taken one at a time on Temperature  

>- Display Regression plot and Summary Statistics
</div>

##  Reactive Server Code 


<div class="green">
    shinyServer(function(input, output) {
    formulaString <- reactive({
        paste("Temp ~ ", input$variable)
    })
    
    fit <- reactive({
        lm(as.formula(formulaString()), data = ToothGrowth)
    })
    
    output$summaryFit <- renderPrint({
        summary(fit())
    })
    
    output$Plot <- renderPlot({
        with(airquality, {
            plot(as.formula(formulaString()), main = formulaString())
            abline(fit(), col = 4)
        })
    })
    })
</div>

## Shiny App and Source code
<div class="green">
>- The app can be accessed here:  https://nishantsisingi.shinyapps.io/New_York_AirQuality/  

>- Github link for the source code : https://github.com/nishantsisingi/Developing-Data-Products-Shiny-Apps
</div>